### 2014-02-05 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/related_work.tex

Correlation based rank is a na\"{i}ve ranking algorithm that ranks
features according to their linear correlation with the output,
i.e.\ Pearson's $r.$ More sophisticated ranking methods include:
\begin{enumerate}
\item The conditional entropy of class $Y$ given feature $X,$
  i.e.\ $H\left(Y|X\right),$ quantifies the amount of information in
  $Y$ that is not provided by $X.$ Subtracting $H\left(Y|X\right)$
  from the entropy of class $Y,$ the information gain of class $Y$
  given feature $X$ is the mutual information between feature $X$ and
  class $Y,$ i.e.\ $I\left(X;Y\right).$
\item The gain ratio of feature $X$ is defined as the information gain
  of feature $X$ normalized against the entropy of itself,
  i.e.\ $\frac{I\left(X;Y\right)}{H\left(X\right)}.$
\item The symmetric uncertainty between feature $X$ and class $Y$
  measures the amount of redundancy between them. It is defined as
  $U\left(X,Y\right)=2\frac{I\left(X;Y\right)}{H\left(X\right)+H\left(Y\right)}.$
\item The Relief method \cite{kira1992feature} evaluates the relevance
  of features to the output class according to how well their values
  distinguish between nearest instances of the same and different
  classes.
\end{enumerate}

>>>>

Correlation based rank is a na\"{i}ve ranking algorithm that ranks
features according to their linear correlation with the output,
i.e.\ Pearson's $r.$ More sophisticated ranking methods include:
\begin{enumerate}
\item The conditional entropy of class $Y$ given feature $X,$
  i.e.\ $H\left(Y|X\right),$ quantifies the amount of information in
  $Y$ that is not provided by $X.$ Subtracting $H\left(Y|X\right)$
  from the entropy of class $Y,$ the information gain of class $Y$
  given feature $X$ is the mutual information between feature $X$ and
  class $Y,$ i.e.\ $I\left(X;Y\right).$
\item The gain ratio of feature $X$ is defined as the mutual information
  of feature $X$ normalized against the entropy of itself,
  i.e.\ $\frac{I\left(X;Y\right)}{H\left(X\right)}.$
\item The symmetric uncertainty between feature $X$ and class $Y$
  measures the amount of redundancy between them. It is defined as
  $U\left(X,Y\right)=2\frac{I\left(X;Y\right)}{H\left(X\right)+H\left(Y\right)}.$
\item The Relief method \cite{kira1992feature} evaluates the relevance
  of features to the output class according to how well their values
  distinguish between nearest instances of the same and different
  classes.
\end{enumerate}
